### 2021-08-28 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
28.08.21.4

The following radar chart allow us to analyze the results for each roaming agreement. Fig.~\ref{fig3} shows a comparison in terms of the common percentage of symbols between compared sub-articles for the Proximus sample roaming agreement. The conclusion that can be reached by simple inspection is that only 11 of the 72 analyzed sub-articles are affected, mostly by the introduction of undesired characters when output file was populated. Similarly, Fig.~\ref{fig4} shows a comparison in terms of the common percentage of words between the sub-articles compared for the Orange sample roaming agreement. In this case, only 7 of the 86 analyzed sub-articles are affected by the introduction of unwanted characters at the time of popularization in the output file, thus improving the results obtained for the Proximus sample roaming agreement.

>>>>

The following radar chart allow us to analyze the results for each roaming agreement. Fig.~\ref{fig3} shows a comparison in terms of the common percentage of symbols between compared sub-articles for the Proximus sample roaming agreement. The conclusion that can be reached by simple inspection is that only 11 of the 72 analyzed sub-articles are affected, mostly by the introduction of undesired characters when output file was populated.

Similarly, Fig.~\ref{fig4} shows a comparison in terms of the common percentage of words between the sub-articles compared for the Orange sample roaming agreement. In this case, only 7 of the 86 analyzed sub-articles are affected by the introduction of undesired characters when the output file is populated, thus improving the results obtained for the Proximus sample roaming agreement.
